Andres Karjus

### 2022-05-11 index.Rmd
news

<div style="text-align: justify; padding-left:1px"> 
I am a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, working on **language and culture dynamics**, using large corpora, machine learning, and human experiments. Recently I have been also working on, through various collaborations, onart history and media industries (stay tuned).
I defended my PhD in 2020, in linguistics at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of University of Edinburgh, on lexical dynamics and communicative needs in language.
I also occasionally teach **stats and data visualization** for the humanities and social sciences (see [more here](https://andreskarjus.github.io/artofthefigure)). On the right is the (of course slightly outdated) photo obligatory for all academic home pages to subtly suggest that in fact I do not spend _all_ my time in the office at all.

@@

Besides research and teaching and consulting and whatnot, I (fortunately) also do other things, which mostly consist of dance (lindy hop, salsa, bachata), boardgames, and outdoorsy stuff (running, hillwalking).

>>>>

<div style="text-align: justify; padding-left:1px"> 
I am a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, working on **language and culture dynamics**, using large corpora, machine learning, and human experiments. Recently I have been also working on, through various collaborations, on art history and creative industries (papers in progress) and advising collaborative projects between involving academic and media industry partners.<br>
I defended my PhD in 2020, in linguistics at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of University of Edinburgh, on lexical dynamics and communicative needs in language.
I also occasionally teach **stats and data visualization** for the humanities and social sciences (see [more here](https://andreskarjus.github.io/artofthefigure)). On the right is the (of course slightly outdated) photo, obligatory for all academic home pages, to subtly suggest that in fact I do not spend _all_ my time in the office at all.

@@

Besides research and teaching and consulting and whatnot, I (fortunately) also do some other things, which mostly consist of dance (lindy hop, salsa, bachata), boardgames, and outdoorsy stuff (running, hillwalking).

### 2022-05-11 news.Rmd
news

- Gave a talk on linguistic corpora and experiments (and media&culture data) at the seminar of the Poncelet laboratory in Moscow (17.11.2021)

>>>>

- Invited talk on language change and big social media data, in the research seminar series of the School of Humanities of Tallinn University (23.02.2022)

- Invited talk on linguistic corpora and experiments (and media&culture data) at the seminar of the Poncelet laboratory in Moscow (17.11.2021)
